Mixed effect tweedie model in TMB

### 2020-06-20 analysis/tmb-sensor-explore/2-fit-temperature.Rmd
other temp models

Current temperature model
```{r}
spde <- make_spde(d_trawl$X, d_trawl$Y, n_knots = 500)
plot_spde(spde)
```

```{r eval = F}
m_temp_rw <- sdmTMB(
  temperature_c ~ 0 + as.factor(year), #+ DOY_scaled + as.factor(ssid)
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  data = d_trawl,
  ar1_fields = TRUE, # changed AR1_field to true
  include_spatial = TRUE, 
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = FALSE
)

saveRDS(m_temp_rw, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-500kn.rds")))
```

Check predictions against raw data
```{r}
predictions <- predict(m_temp_rw)
predictions$residuals <- residuals(m_temp_rw)
cor(predictions$est, predictions$temperature_c)^2 
```

@@

```{r eval=FALSE}
m_temp_rw <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-500kn.rds")))
get_diag(m_temp_rw, response = "temperature_c", variable = "depth_scaled")
```

@@

```{r eval=FALSE}
m_temp3 <- sdmTMB(
  temperature_c ~ 0 + as.factor(year) + SST_scaled * shallow + DOY_scaled * shallow + DOY_scaled2 * shallow,
  data = d_trawl2,
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  ar1_fields = TRUE, include_spatial = TRUE,
  time = "year", spde = spde2, family = gaussian(link = "identity"),
  silent = TRUE
)
```

@@

>>>>

Current temperature model
```{r}
spde <- make_spde(d_trawl$X, d_trawl$Y, n_knots = 800)
plot_spde(spde)
```

```{r eval = F}
m_temp_rw <- sdmTMB(
  temperature_c ~ 0 + as.factor(year), #+ DOY_scaled + as.factor(ssid)
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  data = d_trawl,
  ar1_fields = TRUE, # changed AR1 to true
  include_spatial = TRUE, 
  time = "year", spde = spde, 
  family = gaussian(link = "identity"),
  nlminb_loops = 2,
  newton_steps = 1,
  silent = FALSE
)

saveRDS(m_temp_rw, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn.rds")))
```

Check predictions against raw data
```{r}
m_temp_rw <- readRDS(here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-500kn-2.rds"))
predictions <- predict(m_temp_rw)
predictions$residuals <- residuals(m_temp_rw)
cor(predictions$est, predictions$temperature_c)^2 
```

@@

```{r eval=FALSE}
m_temp_rw <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-500kn-2.rds")))
get_diag(m_temp_rw, response = "temperature_c", variable = "depth_scaled")
```

@@

```{r eval=FALSE}
m_temp2 <- sdmTMB(
  temperature_c ~ 0 + as.factor(year) + DOY_scaled * shallow + DOY_scaled2 * shallow,
  data = d_trawl2,
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  ar1_fields = TRUE, include_spatial = TRUE,
  time = "year", spde = spde2, family = gaussian(link = "identity"),
  nlminb_loops = 2,
  newton_steps = 1,
  silent = TRUE
)

saveRDS(m_temp2, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-DOY.rds")))

m_temp2
```

```{r eval=FALSE}
m_temp3 <- sdmTMB(
  temperature_c ~ 0 + as.factor(year) + SST_scaled * shallow + DOY_scaled * shallow + DOY_scaled2 * shallow,
  data = d_trawl2,
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  ar1_fields = TRUE, include_spatial = TRUE,
  time = "year", spde = spde2, family = gaussian(link = "identity"),
  nlminb_loops = 2,
  newton_steps = 1,
  silent = TRUE
)

saveRDS(m_temp3, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-SST.rds")))

m_temp3
```

@@

```{r eval=FALSE}
get_diag(m_temp3, response = "temperature_c", variable = "depth_scaled")
```
